12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-26 rules/rules17.tex
Fix LaTeX error

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that have been sound (i.e., not
produced any erroneous result) in the corresponding division of the
main track.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \textt{sat}
exceeds the number of checking solvers whose result is \textt{unsat},
or if the unsat-core producing solver is used as a checking solver and
its result is \textt{sat}.  The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.

>>>>

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that have been sound (i.e., not
produced any erroneous result) in the corresponding division of the
main track.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat}
exceeds the number of checking solvers whose result is \texttt{unsat},
or if the unsat-core producing solver is used as a checking solver and
its result is \texttt{sat}.  The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.
